Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-18 appendix.tex
tex

@@

@@

\begin{table*}
\resizebox{\linewidth}{!}{
\setlength{\tabcolsep}{0.47em}
\renewcommand{\arraystretch}{1.1}%
\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
 &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
\hline
\hline
\multirow{6}{*}{CUB} & HM{[}$\mathcal{R},\mathcal{M}${]} & 8 & 27.0 & 36.0 & 13.2 & 42.5 & 19.4 & 48.0 & 22.2 & 32.0 & 0.535 & 0.867 & 11.6 & 10.4 & 19.3 & 2.9 & 35.1\tabularnewline
 & HM{[}$\mathcal{R},g_{\mathsf{B}}(\mathcal{M})${]} & 8 & 24.9 & 33.4 & 12.0 & 41.7 & 21.6 & 45.1 & 24.9 & 29.1 & 0.515 & 0.780 & 12.3 & 12.1 & 19.7 & 3.7 & 37.6\tabularnewline
 & HM{[}$\mathcal{R},0${]} & 8 & 2.4 & 3.8 & 1.1 & 21.7 & 40.8 & 22.3 & 42.2 & 16.7 & 1.000 & 0.000 & 1.6 & 1.2 & 1.7 & 7.0 & 43.9\tabularnewline
 & HM{[}$\mathcal{R},-\gamma/2${]} & 8 & 25.5 & 34.5 & 12.8 & 41.7 & 21.9 & 41.5 & 23.8 & 27.0 & 0.493 & 0.784 & 13.5 & 11.8 & 20.3 & 3.6 & 38.3\tabularnewline
 & HM{[}$\mathcal{R},-\gamma${]} & 8 & 27.5 & 36.5 & 13.5 & 42.5 & 18.1 & 54.0 & 19.9 & 37.5 & 0.561 & 0.925 & 9.9 & 9.7 & 18.6 & 1.7 & 32.2\tabularnewline
 & HM{[}$\mathcal{R},g_{\mathsf{LGA}}${]} & 8 & 24.8 & 33.9 & 12.2 & 41.6 & 21.4 & 45.0 & 21.7 & 31.3 & 0.452 & 0.846 & 13.2 & 12.0 & 20.9 & 4.6 & 37.3\tabularnewline
\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{1/2}}${]} & 8 & 37.7 & 48.5 & 22.0 & 49.2 & 12.6 & 48.6 & 12.3 & 41.3 & 0.562 & 0.825 & 13.5 & 12.9 & 26.9 & 1.8 & 31.7\tabularnewline
\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 38.0 & 48.3 & 21.8 & 49.3 & 12.7 & 46.4 & 11.6 & 39.9 & 0.567 & 0.783 & 16.8 & 11.9 & 27.9 & 1.4 & 32.4\tabularnewline
\multicolumn{1}{c}{} & HM{[}$\mathcal{S},g_{\mathsf{2}}${]} & 8 & 37.4 & 48.2 & 17.1 & 49.2 & 12.9 & 45.1 & 13.2 & 39.1 & 0.599 & 0.738 & 17.7 & 12.8 & 27.5 & 1.9 & 33.1\tabularnewline
\multicolumn{1}{c}{} & LGA u=2.2 &  & 34.8 & 45.5 & 15.2 & 47.1 & 13.4 & 36.0 & 17.2 & 26.1 & 0.934 & 0.244 & 20.1 & 15.9 & 27.3 & 3.8 & 36.1\tabularnewline
\end{tabular}}
\end{table*}

\begin{table*}
\resizebox{\linewidth}{!}{
\setlength{\tabcolsep}{0.3em}
\renewcommand{\arraystretch}{1.1}%
\begin{tabular}{ccc|cccc|ccccc|ccccc|c}
\hline
\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
 &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
\hline
{*} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]} & 8 & 35.5 & 46.3 & 20.3 & 47.5 & 14.6 & 41.1 & 14.3 & 34.5 & 0.530 & 0.739 & 18.1 & 13.1 & 27.9 & 2.1 & 35.3\tabularnewline
 & +0.5i aap & 8 & 34.8 & 45.2 & 19.8 & 47.6 & 15.6 & 35.9 & 18.5 & 28.2 & 0.802 & 0.447 & 19.2 & 13.9 & 26.3 & 2.9 & 36.4\tabularnewline
 & +i aap & 8 & 34.7 & 45.6 & 19.5 & 46.9 & 16.9 & 34.2 & 18.9 & 26.7 & 0.904 & 0.296 & 20.4 & 16.1 & 26.6 & 4.2 & 37.3\tabularnewline
 & +i aap aan){*}1.0 & 8 & 34.2 & 44.7 & 19.3 & 47.9 & 15.2 & 35.2 & 18.0 & 27.1 & 0.902 & 0.301 & 17.9 & 15.0 & 28.5 & 3.0 & 36.3\tabularnewline
 & +i aa\textasciitilde p apn\textasciitilde{} 1.0 & 8 & 37.9 & 49.4 & 22.5 & 49.2 & 12.9 & 45.9 & 15.0 & 38.9 & 0.909 & 0.378 & 14.8 & 11.7 & 25.3 & 0.9 & 31.4\tabularnewline
 & ICS gamma 0.2 &  & 35.8 & 46.6 & 16.4 & 48.3 & 13.2 & 39.9 & 12.7 & 33.3 & 0.775 & 0.507 & 15.9 & 14.9 & 27.2 & 2.7 & 33.6\tabularnewline
\end{tabular}}
\end{table*}

>>>>

\begin{table*}
\resizebox{\linewidth}{!}{
\setlength{\tabcolsep}{0.47em}
\renewcommand{\arraystretch}{1.1}%
\begin{tabular}{c|cc|cccc|ccccc|ccccc|c}
	\toprule
\multicolumn{1}{c|}{\multirow{2}{*}{\textbf{Dataset}}} & \multirow{2}{*}{\textbf{Defense}} & \multirow{2}{*}{$\eta$} & \multicolumn{4}{c|}{\textbf{Benign Example}} & \multicolumn{10}{c|}{\textbf{White-Box Attacks for Robustness Evaluation}} & \multirow{2}{*}{\textbf{ERS$\uparrow$}}\tabularnewline
\cline{4-17} \cline{5-17} \cline{6-17} \cline{7-17} \cline{8-17} \cline{9-17} \cline{10-17} \cline{11-17} \cline{12-17} \cline{13-17} \cline{14-17} \cline{15-17} \cline{16-17} \cline{17-17}
 &  &  & R@1$\uparrow$ & R@2$\uparrow$ & mAP$\uparrow$ & NMI$\uparrow$ & CA+$\uparrow$ & CA-$\downarrow$ & QA+$\uparrow$ & QA-$\downarrow$ & TMA$\downarrow$ & ES:D$\downarrow$ & ES:R$\uparrow$ & LTM$\uparrow$ & GTM$\uparrow$ & GTT$\uparrow$ & \tabularnewline
 \midrule
\multirow{2}{*}{CUB} & HM{[}$\mathcal{S},g_{\mathsf{LGA}}${]}\&ICS & 8 & 37.2 & 47.8 & 21.4 & 48.4 & 12.9 & 40.9 & 14.7 & 33.7 & 0.806 & 0.487 & 17.1 & 13.2 & 26.3 & 2.3 & 33.5\tabularnewline
& HM[$\mathcal{S},g_\mathsf{LGA}$]\&$L_\text{ICS}(\cdots;\gamma=0.2)$ & 8 & 35.8 & 46.6 & 16.4 & 48.3 & 13.2 & 39.9 & 12.7 & 33.3 & 0.775 & 0.507 & 15.9 & 14.9 & 27.2 & 2.7 & 33.6\tabularnewline
 \bottomrule
\end{tabular}}
	\caption{The margin parameter is set to $0$ in order to avoid negative effect.
	%
	R@1 performance drops with marginal robustness gain.}
	\label{tab:0margin}
\end{table*}

@@

The margin parameter is set to $0$ in order to avoid negative effect in $L_\text{ICS}$,
as shown in \cref{tab:0margin}.

@@
